Extreme Value Chapter 3

### 2022-03-01 Ch3_samplesize/Figures_Ch3.Rmd
Trying to knit this but is going slow.

# TEST VALUES --------------------------------------
## Thresholds ----------------
# Thresholds based on quantiles: because when we have a sample, we still don't know the truth
# But we can know the quantiles of our sample.
# summary(truth_df$x_samps)
# thresh_tests <- round(quantile(truth_df$x_samps, c(0.5, 0.75, 0.9, 0.99, 0.999, 0.9999), names = FALSE))
tru_n <- 50000
w_samp_sizes <- pis*tru_n

@@

```{r}
thetas %>% 
  knitr::kable()
write.csv(thetas, file = "Ch3_samplesize/Figures/table1.csv")
```

>>>>

# TEST VALUES --------------------------------------
## Thresholds ----------------
# Thresholds based on quantiles: because when we have a sample, we still don't know the truth
# But we can know the quantiles of our sample.
# summary(truth_df$x_samps)
# thresh_tests <- round(quantile(truth_df$x_samps, c(0.5, 0.75, 0.9, 0.99, 0.999, 0.9999), names = FALSE))
tru_n <- 50000
pis <- c( 0.1, 0.2, 0.3, 0.4)
w_samp_sizes <- pis*tru_n

@@

```{r}
thetas %>% 
  knitr::kable()
# write.csv(thetas, file = "Ch3_samplesize/Figures/table1.csv")
```
